Response to the Reviewers' Comments

### 2018-07-30 response to reviewers/letter.tex
Revised the comments again.

We  merged Section III and Section IV as the reviewer advised. We also revised the titles of Sections: \textcolor{red}{I. Challenges in EV Efficiency Enhancement, II. Challenges in EV Efficiency Enhancement, and III. Design-Time Optimization of Electric Vehicles} focusing on the design-time optimization of electric vehicles. Now Sections II and III mainly explain the challenges and opportunities of EV power management with a conclusion such that personalized powertrain synthesis is promising for further push to EV power consumption saving.
Please see the following modification.\\

@@

\item [C3: ] From the perspective of the vehicle manufacturers, the major benefit to limits the offered configurations for a particular model is to boost the yield and minimize the average cost per vehicle. Fully customizing the configuration on an individual basis places a very high requirement on the supply side that may have to fundamentally change the current way to produce and assemble vehicles to accommodate such need. This can lead to significant manufacturing cost increase for which the customers have to pay eventually. 
\item [R3: ] Currently, almost all vehicle manufacturers provide drivetrain options (engine, motor and battery size) for the same modeles of vehicles. This concept is more emphasized and more easier to implement for electric vehicles. Please watch the following video presented by BMW from 40 seconds to 1 minute 40 seconds from BMW: \\
https://www.youtube.com/watch?v=xvaQMTcckSg, \\
which emphasizes various battery capacity and motor capacity configurations. We already described this in Section V of the original manuscript as follow:\\

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\textbf{[REVIEWER 2]}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{description}
\item [C1: ] Sections I -- IV are not very focused and do not provide a great introduction into the tool that is presented. It starts by talking about pollution, misleading MPGe numbers, trying to enhance energy efficiency of vehicles, electric vehicle charging demand problems, and materials used to create the car and potential repair costs as potential issues with electric vehicles. But as far as I can tell, the main thing that tool provides is a way for consumers to easily choose vehicle options based on their user requirements and these sections should be focused on this. I had no idea what the paper was about until the tool was presented.
\item [R1: ] We thank to the reviewer to provide such a valuable comment. We merged Section III and Section IV. We also revised the titles of Sections: I. Challenges in EV Efficiency Enhancement, II. Challenges in EV Efficiency Enhancement, and III. Design-Time Optimization of Electric Vehicles, focusing on the design-time optimization of electric vehicles. Now Sections II and III mainly explain the challenges in the conventional EV power efficiency enhancement and opportunities of the proposed EV power management; the personalized powertrain synthesis is promising for further push to EV power consumption saving. We relocated and revised the last paragraph in Section I and keep focus on the demand for higher-efficiency electric vehicles.

We performed major revision in Sections II and III (previously Sections II and IV.)

@@

\underline{We reflect reviewer's comment in the fifth paragraph in Section V as:}\\

>>>>

We  merged Section III and Section IV as the reviewer advised. We also revised the titles of Sections: \textcolor{red}{I. Challenges in EV Efficiency Enhancement, II. Challenges in EV Efficiency Enhancement, and III. Design-Time Optimization of Electric Vehicles} focusing on the design-time optimization of electric vehicles. Now Sections II and III mainly explain the challenges in the conventional EV power efficiency enhancement and opportunities of the proposed EV power management; the personalized powertrain synthesis is promising for further push to EV power consumption saving. We relocated and revised the last paragraph in Section I and keep focus on the demand for higher-efficiency electric vehicles.
\\

@@

\item [C3: ] From the perspective of the vehicle manufacturers, the major benefit to limits the offered configurations for a particular model is to boost the yield and minimize the average cost per vehicle. Fully customizing the configuration on an individual basis places a very high requirement on the supply side that may have to fundamentally change the current way to produce and assemble vehicles to accommodate such need. This can lead to significant manufacturing cost increase for which the customers have to pay eventually. 
\item [R3: ] Currently, almost all vehicle manufacturers provide drivetrain options (engine, motor and battery size) for the same models of vehicles. This concept is more emphasized and more easier to implement for electric vehicles. Please watch the following video presented by BMW from 40 seconds to 1 minute 40 seconds (by BMW): \\
https://www.youtube.com/watch?v=xvaQMTcckSg, \\
which emphasizes various battery capacity and motor capacity configurations. We already described this in Section V of the original manuscript as follow:\\

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\textbf{[REVIEWER 2]}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{description}
\item [C1: ] Sections I -- IV are not very focused and do not provide a great introduction into the tool that is presented. It starts by talking about pollution, misleading MPGe numbers, trying to enhance energy efficiency of vehicles, electric vehicle charging demand problems, and materials used to create the car and potential repair costs as potential issues with electric vehicles. But as far as I can tell, the main thing that tool provides is a way for consumers to easily choose vehicle options based on their user requirements and these sections should be focused on this. I had no idea what the paper was about until the tool was presented.
\item [R1: ] We thank to the reviewer to provide such a valuable comment. We relocated and revised the last paragraph in Section I and keep focus on the demand for higher-efficiency electric vehicles. We performed major revision in Sections II and III (previously Sections II to IV). We merged Section III and Section IV. We also revised the titles of Sections: I. Challenges in EV Efficiency Enhancement, II. Challenges in EV Efficiency Enhancement, and III. Design-Time Optimization of Electric Vehicles, focusing on the design-time optimization of electric vehicles. Now Sections II and III mainly explain the challenges in the conventional EV power efficiency enhancement and opportunities of the proposed EV power management; the personalized powertrain synthesis is promising for further push to EV power consumption saving.

@@

\underline{We reflected the reviewer's comment in the fifth paragraph of Section V as follows:}
